---
title: "DA_Project"
author: "Ashiq"
date: "12/11/2021"
output: html_document
---

## Questions
1. How many variables did Lasso and Horseshoe select?
2. Which of the two methods leads to a sparser solution?
3. Can you guess the reason?
4. Apply different sparse regression (regularization/shrinkage/dimension reduction technique) on this data. See table 1 and 2 of Bhadra et al. (2019) for a list of popular regularization methods and Bayesian methods. All of them are for similar problems in sparse signal recovery. The same paper has a list of R packages for implementing Bayesian methods in Table 5.
5. Compare between different methods? e.g. Would Elastic Net or MCP or Dantzig Selector be a better fit than Lasso? Do concave methods outperform convex regularization methods? How do you test? How about Bayesian methods or PC Regression? Choose any two methods that you like.

## Answers
1 & 2.
<table>
 <thead>
  <tr>
   <th style="text-align:left;"> Regression Method </th>
   <th style="text-align:left;"> MSE </th>
   <th style="text-align:left;"> # of variables selected </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> LASSO </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;">  </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Horseshoe </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;"> </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Sparse Net </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;"> </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Elastic Net </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;"> </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Bayesian LASSO </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;"> </td>
  </tr>
  <tr>
   <td style="text-align:left;"> MCP </td>
   <td style="text-align:right;">  </td>
   <td style="text-align:right;"> </td>
  </tr>
</tbody>
</table>

3. Reasons:

4. Codes:

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
5. a) Would Elastic Net or MCP or Dantzig Selector be a better fit than Lasso?

b) Do concave methods outperform convex regularization methods? How do you test?

c) How about Bayesian methods or PC Regression?

